Secure Composition of Robust and Optimising Compilers

### 2023-06-14 popl/main.tex
Wording
Get rid of we, our, us

\BrText{Solution}{
% keyword: pass
\MPin{
	commands missing
}
This paper introduces a framework for reasoning about the composition of secure and optimising compiler passes and it showcases the power of this framework by instantiating it on a multi-pass compilation chain.
To this end, this paper first discusses how to compose security properties, such as temporal and spatial memory safety into general memory safety, and cryptographic constant time.
Then, this paper defines several secure compiler passes, where each is either preserving a different security property (e.g., temporal or spatial memory safety) or performing a security-preserving optimisation, (e.g., applying constant-folding or dead-code elimination).
% keyword- end to end, composition
Finally, this paper shows how to compose these secure compiler passes into a multi-pass compilation chain which can be proven to provide end-to-end preservation of general memory safety and cryptographic constant time.
\MKin{
  ,,can be proven'' -> is proven (?)
}
Crucially, this end-to-end security preservation is obtained by having each compilation pass (i) preserve a sub-part of the overall security property individually and then (ii) compose each preserved security property as dictated by our framework.
Our results showcase how our framework allows the kind of formal security reasoning that compiler writers already want (and do), obtaining precise, compositional security reasoning while providing minimal (and modular) proof effort.
\MPin{
	last line: not the best.
}
}

@@

  \item %
        % \Cref{sec:casestud} sets up a case-study to demonstrate the power of our formal framework.
        A case-study demonstrating the power of our formal framework (\Cref{sec:casestud}).
        %We define several different languages and compilers between them and prove that the compilers are robustly preserving different properties.
        To this end, a compilation chain of several passes is presented.
        %The sequential composition of these compilers yields a compilation chain that is optimizing and robustly preserving a combination of \gls{ms} and \gls{cct}.
        The chain attains a combination of \gls{ms} and \gls{cct} by means of applying the theoretical work from the previous contribution on the individual, secure passes concerning \gls{tms}, \gls{sms}, and \gls{scct}, respectively.
        %As for optimizations, the chain has two passes, one performing \gls{cf} and the other \gls{dce}.
        Furthermore, the chain entails two passes for \gls{ms}\MKin{maybe patch \gls{ms} when optimizing passes are done} that are optimizing: One performs a simple \gls{dce} and the other \gls{cf}.
        %This compilation chain demonstrates the ability to perform modular proof engineering by leaveraging this paper's compositionality theorems.
        This demonstrates that the usage of the presented framework is both simpler and more expressive compared to one monolithic security proof of the whole compilation chain.

  \item Our key contributions are formalized in the Coq proof assistant.
        The practically relevant parts of the formalization are \emph{extractable}.
        That is, one can translate the Coq code to Ocaml and run the compilation chain from the previous contribution.
        Finally, in this paper, whenever definitions or proofs are done in Coq, we use the symbol \CoqSymbol.
\end{itemize}}

@@

\contribution{Open Source \& Technical Report} Our technical report and the Coq formalisation are available as supplementary material.\MKin{cite/link}

@@

\emph{Events} $\event$ are an abstract representation of observable actions a program can do during its execution.
Typically, one always has an empty observation $\emptyevent$ used to represent unimportant actions.
A sequence of events $\trace$ is a \emph{trace}.
So, throughout the paper, we use $\overline{\cdot}$ to mark meta-variables as sequences.
Empty sequences are denoted with $\hole{\cdot}$ and concatenation of traces $\trace[_{1}],\trace[_{2}]$ is written as $\trace[_{1}]\cdot\trace[_{2}]$.
For sake of brevity, we use this notation also for pre- and appending events to traces.

A trace-based property $\pi$ is a set of admissable traces.
For a trace to be admissable, a predicate evaluates to true whenever $\trace\in\pi$.
Classes of properties $\class$, commonly referred to as hyperproperties in literature, are sets of properties.
The \emph{lifting} of a property $\pi$ is simply its powerset and denoted as $\lift{\pi}$.
To define property satisfaction, we first look at programming languages.

For languages used in this paper, we consider a small-step style semantics.
That is, there is a step relation between states $\statevar$ and an event $\event$: $\stepto[]{\statevar[_{1}]}{\statevar[_{2}]}{\event}$.
Also, a program's syntax $p$ is encoded in the state $\statevar$ which we write as $p\in\statevar$.
For states $\statevar$, we assume there exists a judgement $\isval{\statevar}$ that determines wether $\statevar$ is a final state or not.
\Cref{fig:starstep:and:nstep}\MK{appendix?} defines the star-step relation $\stepto{\statevar[_{1}]}{\statevar[_{2}]}{\trace}$, essentially modelling a big-step style evaluation, and the $n$-step relation $\stepton{\statevar[_{1}]}{\statevar[_{2}]}{\trace}$ that evaluates a program for $n$ steps.
Both relations filter $\varepsilon$ events.

@@

  \caption{Star-step and $n$-step relation for a given step relation $\stepto{\statevar[_{1}]}{\statevar[_{2}]}{\event}$}\label{fig:starstep:and:nstep}
\end{figure}
%
The \emph{behavior} of a whole program $w$ ($\behav{w}$) is a set containing all traces the program may emit during execution.
Note that for deterministic languages, $\behav{w}$ is a singleton set for any $w$.
With this, we can define satisfaction:

@@

Partial programs cannot be executed, because they lack definitions for some symbols.
Providing definitions for symbols is usually the job of the \emph{linker}.
We denote linking two programs $\progvar[_{1}],\progvar[_{2}]$ as $\link{\progvar[_{1}]}{\progvar[_{2}]}$.
For sake of simplicity, we assume that linking does not fail.
With linking, we can define robust satisfaction analogously to \Cref{def:propsat,def:classsat}:

\begin{definition}[Robust Property Satisfaction]\label{def:proprsat}
  A program $\progvar$ robustly satisfies $\pi$ ($\rsat{\progvar}{\pi}$) iff for any program $\contextvar$ we have $\sat{\link{\contextvar}{\progvar}}{\pi}$. (similarily for $\rsat{\progvar}{\class}$)
\end{definition}

@@

We expect compilers to preserve robust satisfaction.
In this paper, compilers are modelled as function from one programming language's syntax to the other.
Since this paper considers composing compilers, we'll adopt notation similar to tombstone diagrams to easen the formal burden.
So, we denote a compiler from $\src{L}$ to $\trg{L}$ as $\cc{\src{L}\to\trg{L}}{\src{\bullet}}$ and we refer to $\src{L}$ as \emph{source} language and to $\trg{L}$ as \emph{target} language.
Composing $\cc{\src{L}\to\trg{L}}{\src{\bullet}}$ with $\cc{\trg{L}\to\obj{L}}{\trg{\bullet}}$ is denoted as $\cc{\src{L}\to\trg{L}\to\obj{L}}{\src{\bullet}}$ and means first running $\cc{\src{L}\to\trg{L}}{\src{\bullet}}$ and plugging the output into $\cc{\trg{L}\to\obj{L}}{\trg{\bullet}}$.
Contrary to tombstones, we don't consider a compiler's implementation language.
We now define the compiler-property robust trace-property preservation.

@@

\section{Composing Properties}\label{sec:compprop}
\Cref{subsec:propdefs} introduces a ,,most general'' trace model and defines properties (\gls{tms}, \gls{sms}, \gls{ms}, and \gls{cct}) that our case study (\Cref{sec:casestud}) uses.
By means of taking these properties as an example, \Cref{subsec:monitors} defines monitors for them and an agreement relation between a monitor's trace model with the most general trace model.
Then, we define monitor-based satisfaction and we prove that trace-property satisfaction is implied by it.
Since monitor-based satisfaction is easier to reason about, this makes our later proofs considerably simpler.

@@

Security tags describe wether an event contains sensitive information ($\lock$) or not ($\unlock$).
Control tags state wether the context ($\ctx$) or the component ($\comp$) are responsible for emitting the event.
Pre-events describe the actual kind of event that happened.
$\ev{Alloc\ \loc\ n}$ states that an allocation of size $n$ happened and is stored at $\loc$.
Locations $\loc$ are elements of $L$ and left abstract.
However, we expect $L$ to be closed over addition with natural numbers.
$\ev{Dealloc\ \loc}$ announces that location $\loc$ is freed.
$\ev{Use\ \loc\ n}$ abstracts over reads from $\loc$ and writes to $\loc$ in memory, where $n$ is read/written, respectively.
$\ev{Branch\ n}$ and $\ev{Binop\ n}$ leak values involved in a branch or in a binary operation with data-dependent execution time.
Finally, events are either the emptyevent ($\emptyevent$), a program crash ($\lightning$), or a tuple consisting of a pre-event, a control tag, and a security tag.

We use this trace model to define any property that interests us.
In a sense the trace model is most general, because it abstracts all events done in our languages as defined in \Cref{sec:casestud}.
We write $\event[_{1}]\le_{\trace}\event[_{2}]$ if $\event[_{1}]$ occurs at an earlier position in $\trace$ than $\event[_{2}]$.

@@

We define a variant of the \gls{cct} security property.
Generally, one cannot define \gls{cct} just as trace-property without, e.g., performing a self-composition of a program.
That's why we adopt for a stricter variant of \gls{cct}, called \gls{scct}, that enforces common policies to ensure code is \gls{cct}.
For example, one must not branch on secrets or perform binary operations, such as division, on secrets whose timing is data-dependent.
We opt for a definition that disregards any secrets leaked on a trace.
To define the property, we need a function on traces that strips all events with a $\lock$-tag: $\downarrow_{\lock}(\cdot)$.

@@

This subsection presents monitors for our properties of interest (\gls{tms}, \gls{sms}, \gls{ms}, \gls{scct}).
Each monitor $\monitor$ has its own accompanying trace model that abstracts over our most general trace model.
%This is because monitors should only be concerned with property-relevant information.
Traces of the accompanying trace model are written as $\abstrace$ and $\monitorcheck{\monitor}{\monitor[']}{\abstrace}$ is the notation for the semantics of a monitor.
The empty monitor is denoted as $\emptyset$.
For each model of a monitor, an agreement relation $\traceagree{\pi}{\trace}{\abstrace}$ is defined that relates monitor specific traces with most general traces.
The notation $\traceagree[]{\pi}{\event}{\absevent}$ is used to relate just events and the star version of it is defined similarily to \Cref{fig:starstep:and:nstep}.
With this, first, monitor satisfaction is defined and then the individual monitors.
Finally, for every monitor, it is shown that monitor satisfaction implies trace property satisfaction.

@@

\section{Case Study: Memory Safe and Cryptographic Constant Time Code}\label{sec:casestud}
This section defines several secure compilers, each of which robustly preserves a different property of interest.
We demonstrate the power of our framework from \Cref{sec:compprop,sec:compcomp} by composing these compilers for a secure, but optimizing, compilation chain that robustly preserves \gls{ms} and \gls{cct}.
Concretely, \Cref{subsec:cs:tms} starts by defining languages $\src{L_{TMS}}$ and $\trg{L}$ and describes a compiler $\cc{\src{L_{TMS}}\to\trg{L}}{\src{\bullet}}$ for the robust preservation of \gls{tms} between the two languages.
\Cref{subsec:cs:ms} defines $\irl{L_{MS}}$ and a compiler $\cc{\trg{L}\to\irl{L_{MS}}}{\trg{\bullet}}$ that robustly preserves \gls{sms}.
By the framework presented in \Cref{sec:compcomp,sec:compprop}, we attain a compiler $\cc{\src{L_{TMS}}\to\irl{L_{MS}}}{\src{\bullet}}$ for the robust preservation of \gls{ms} by composing $\cc{\src{L_{TMS}}\to\trg{L}}{\src{\bullet}}$ and $\cc{\trg{L}\to\irl{L_{MS}}}{\trg{\bullet}}$.
\Cref{subsec:cs:scct} defines $\obj{L_{CCT}}$ and a compiler $\cc{\irl{L_{MS}}\to\obj{L_{CCT}}}{\irl{\bullet}}$ that robustly preserves \gls{cct}.
Composing it with $\cc{\src{L_{TMS}}\to\irl{L_{MS}}}{\src{\bullet}}$ yields $\cc{\src{L_{TMS}}\to\obj{L_{CCT}}}{\src{\bullet}}$, a compiler that robustly preserves a combination of \gls{ms} and \gls{cct}.
We attain our final compilation chain in \Cref{subsec:cs:opts}, which defines optimizing compilers performing either \gls{cf} or \gls{dce} and composes them with $\cc{\src{L_{TMS}}\to\obj{L_{CCT}}}{\src{\bullet}}$, giving us an optimizing, secure compilation chain.

>>>>

\BrText{Solution}{
% keyword: pass
\MPin{
	commands missing
}
This paper introduces a framework for reasoning about the composition of secure and optimising compiler passes and it showcases the power of this framework by instantiating it on a multi-pass compilation chain.
To this end, this paper first discusses how to compose security properties, such as temporal and spatial memory safety into general memory safety, and cryptographic constant time.
Then, this paper defines several secure compiler passes, where each is either preserving a different security property (e.g., temporal or spatial memory safety) or performing a security-preserving optimisation, (e.g., applying constant-folding or dead-code elimination).
% keyword- end to end, composition
Finally, this paper shows how to compose these secure compiler passes into a multi-pass compilation chain which can be proven to provide end-to-end preservation of general memory safety and cryptographic constant time.
\MKin{
  ,,can be proven'' -> is proven (?)
}
Crucially, this end-to-end security preservation is obtained by having each compilation pass (i) preserve a sub-part of the overall security property individually and then (ii) compose each preserved security property as dictated by the framework of this paper.
The results showcase how the framework allows the kind of formal security reasoning that compiler writers already want (and do), obtaining precise, compositional security reasoning while providing minimal (and modular) proof effort.
\MPin{
	last line: not the best.
}
}

@@

  \item %
        % \Cref{sec:casestud} sets up a case-study to demonstrate the power of our formal framework.
        A case-study demonstrating the power of the formal frameworks from the previous contributions (\Cref{sec:casestud}).
        %We define several different languages and compilers between them and prove that the compilers are robustly preserving different properties.
        To this end, a compilation chain of several passes is presented.
        %The sequential composition of these compilers yields a compilation chain that is optimizing and robustly preserving a combination of \gls{ms} and \gls{cct}.
        The chain attains a combination of \gls{ms} and \gls{cct} by means of applying the theoretical work from the previous contribution on the individual, secure passes concerning \gls{tms}, \gls{sms}, and \gls{scct}, respectively.
        %As for optimizations, the chain has two passes, one performing \gls{cf} and the other \gls{dce}.
        Furthermore, the chain entails two passes for \gls{ms}\MKin{maybe patch \gls{ms} when optimizing passes are done} that are optimizing: One performs a simple \gls{dce} and the other \gls{cf}.
        %This compilation chain demonstrates the ability to perform modular proof engineering by leaveraging this paper's compositionality theorems.
        This demonstrates that the usage of the presented framework is both simpler and more expressive compared to one monolithic security proof of the whole compilation chain.

  \item The key contributions are formalized in the Coq proof assistant.
        The practically relevant parts of the formalization are \emph{extractable}.
        That is, one can translate the Coq code to Ocaml and run the compilation chain from the previous contribution.
        Finally, this paper indicates with \CoqSymbol whenever definitions or proofs are done in Coq.
\end{itemize}}

@@

\contribution{Open Source \& Technical Report} A technical report and the Coq formalisation are available as supplementary material.\MKin{cite/link}

@@

\emph{Events} $\event$ are an abstract representation of observable actions a program can do during its execution.
Typically, one always has an empty observation $\emptyevent$ used to represent unimportant actions.
A sequence of events $\trace$ is a \emph{trace}.
So, throughout the paper, $\overline{\cdot}$ is used to mark meta-variables as sequences.
Empty sequences are denoted with $\hole{\cdot}$ and concatenation of traces $\trace[_{1}],\trace[_{2}]$ is written as $\trace[_{1}]\cdot\trace[_{2}]$.
For sake of brevity, this notation also used for pre- and appending events to traces.

A trace-based property $\pi$ is a set of admissable traces.
For a trace to be admissable, a predicate evaluates to true whenever $\trace\in\pi$.
Classes of properties $\class$, commonly referred to as hyperproperties in literature, are sets of properties.
The \emph{lifting} of a property $\pi$ is simply its powerset and denoted as $\lift{\pi}$.
To define property satisfaction it is integral to first look at programming languages.

For languages used in this paper, a small-step style semantics is used.
That is, there is a step relation between states $\statevar$ and an event $\event$: $\stepto[]{\statevar[_{1}]}{\statevar[_{2}]}{\event}$.
Also, a program's syntax $p$ is encoded in the state $\statevar$ which is written as $p\in\statevar$.
For states $\statevar$, it is assumed that there exists a judgement $\isval{\statevar}$ that determines wether $\statevar$ is a final state or not.
\Cref{fig:starstep:and:nstep}\MK{appendix?} defines the star-step relation $\stepto{\statevar[_{1}]}{\statevar[_{2}]}{\trace}$, essentially modelling a big-step style evaluation, and the $n$-step relation $\stepton{\statevar[_{1}]}{\statevar[_{2}]}{\trace}$ that evaluates a program for $n$ steps.
Both relations filter $\varepsilon$ events.

@@

  \caption{Star-step and $n$-step relation for a given step relation $\stepto{\statevar[_{1}]}{\statevar[_{2}]}{\event}$}\label{fig:starstep:and:nstep}
\end{figure}
%
The \emph{behavior} of a whole program $w$ ($\behav{w}$) is a set containing all traces the program may emit during execution.
Note that for deterministic languages, $\behav{w}$ is a singleton set for any $w$.
The behavior of programs gives rise to the definition of satisfaction:

@@

Partial programs cannot be executed, because they lack definitions for some symbols.
Providing definitions for symbols is usually the job of the \emph{linker}.
Notationally, linking two programs $\progvar[_{1}],\progvar[_{2}]$ is written $\link{\progvar[_{1}]}{\progvar[_{2}]}$.
For sake of simplicity, linking does not fail.
With linking, it is possible to define robust satisfaction analogously to \Cref{def:propsat,def:classsat}:

\begin{definition}[Robust Property Satisfaction]\label{def:proprsat}
  A program $\progvar$ robustly satisfies $\pi$ ($\rsat{\progvar}{\pi}$) iff for any program $\contextvar$ it holds that $\sat{\link{\contextvar}{\progvar}}{\pi}$. (similarily for $\rsat{\progvar}{\class}$)
\end{definition}

@@

It is expected that compilers preserve robust satisfaction.
In this paper, compilers are modelled as function from one programming language's syntax to the other.
Since this paper considers composing compilers, we'll adopt notation similar to tombstone diagrams\MK{cite} to easen the formal burden.
So, denote a compiler from $\src{L}$ to $\trg{L}$ as $\cc{\src{L}\to\trg{L}}{\src{\bullet}}$ and refer to $\src{L}$ as \emph{source} language and to $\trg{L}$ as \emph{target} language.
Composing $\cc{\src{L}\to\trg{L}}{\src{\bullet}}$ with $\cc{\trg{L}\to\obj{L}}{\trg{\bullet}}$ is denoted as $\cc{\src{L}\to\trg{L}\to\obj{L}}{\src{\bullet}}$ and means first running $\cc{\src{L}\to\trg{L}}{\src{\bullet}}$ and plugging the output into $\cc{\trg{L}\to\obj{L}}{\trg{\bullet}}$.
Contrary to tombstones, the implementation language of a compiler is disregarded.
Now, define the compiler-property robust trace-property preservation.

@@

\section{Composing Properties}\label{sec:compprop}
\Cref{subsec:propdefs} introduces a ,,most general'' trace model and defines properties (\gls{tms}, \gls{sms}, \gls{ms}, and \gls{cct}) that the case study (\Cref{sec:casestud}) uses.
By means of taking these properties as an example, \Cref{subsec:monitors} defines monitors for them and an agreement relation between a monitor's trace model with the most general trace model.
Then, monitor-based satisfaction is introduced and it is proven that trace-property satisfaction is implied by it.
Since monitor-based satisfaction is easier to reason about, this simplifies later proofs considerably.

@@

Security tags describe wether an event contains sensitive information ($\lock$) or not ($\unlock$).
Control tags state wether the context ($\ctx$) or the component ($\comp$) are responsible for emitting the event.
Pre-events describe the actual kind of event that happened.
$\ev{Alloc\ \loc\ n}$ states that an allocation of size $n$ happened and is stored at $\loc$.
Locations $\loc$ are elements of $L$ and left abstract.
However, it is expected that $L$ is closed over addition with natural numbers.
$\ev{Dealloc\ \loc}$ announces that location $\loc$ is freed.
$\ev{Use\ \loc\ n}$ abstracts over reads from $\loc$ and writes to $\loc$ in memory, where $n$ is read/written, respectively.
$\ev{Branch\ n}$ and $\ev{Binop\ n}$ leak values involved in a branch or in a binary operation with data-dependent execution time.
Finally, events are either the emptyevent ($\emptyevent$), a program crash ($\lightning$), or a tuple consisting of a pre-event, a control tag, and a security tag.

This trace model is used to define any property of interest.
In a sense, the trace model is most general, because it abstracts all events done in the languages as defined in \Cref{sec:casestud}.
This papers uses $\event[_{1}]\le_{\trace}\event[_{2}]$ if $\event[_{1}]$ occurs at an earlier position in $\trace$ than $\event[_{2}]$.

@@

A variant of the \gls{cct} security property is defined.
Generally, one cannot define \gls{cct} just as trace-property without, e.g., performing a self-composition of a program.
That is why this paper adopts a stricter variant of \gls{cct}, called \gls{scct}, that enforces common policies to ensure code is \gls{cct}.
For example, one must not branch on secrets or perform binary operations, such as division, on secrets whose timing is data-dependent.
Even stronger, \gls{scct} disregards any secrets leaked on a trace.
To define the property, a function on traces is needed that strips all events with a $\lock$-tag: $\downarrow_{\lock}(\cdot)$.

@@

This subsection presents monitors for properties \gls{tms}, \gls{sms}, \gls{ms}, and \gls{scct}.
Each monitor $\monitor$ has its own accompanying trace model that abstracts over the most general trace model.
%This is because monitors should only be concerned with property-relevant information.
Traces of the accompanying trace model are written as $\abstrace$ and $\monitorcheck{\monitor}{\monitor[']}{\abstrace}$ is the notation for the semantics of a monitor.
The empty monitor is denoted as $\emptyset$.
For each model of a monitor, an agreement relation $\traceagree{\pi}{\trace}{\abstrace}$ is defined that relates monitor specific traces with most general traces.
The notation $\traceagree[]{\pi}{\event}{\absevent}$ is used to relate just events and the star version of it is defined similarily to \Cref{fig:starstep:and:nstep}.
With this, first, monitor satisfaction is defined and then the individual monitors.
Finally, for every monitor, it is shown that monitor satisfaction implies trace property satisfaction.

@@

\section{Case Study: Memory Safe and Cryptographic Constant Time Code}\label{sec:casestud}
This section defines several secure compilers, each of which robustly preserves a different property of interest.
The power of the frameworks from \Cref{sec:compprop,sec:compcomp} is demonstrated by composing these compilers for a secure, but optimizing, compilation chain that robustly preserves \gls{ms} and \gls{cct}.
Concretely, \Cref{subsec:cs:tms} starts by defining languages $\src{L_{TMS}}$ and $\trg{L}$ and describes a compiler $\cc{\src{L_{TMS}}\to\trg{L}}{\src{\bullet}}$ for the robust preservation of \gls{tms} between the two languages.
\Cref{subsec:cs:ms} defines $\irl{L_{MS}}$ and a compiler $\cc{\trg{L}\to\irl{L_{MS}}}{\trg{\bullet}}$ that robustly preserves \gls{sms}.
By the framework presented in \Cref{sec:compcomp,sec:compprop}, a compiler $\cc{\src{L_{TMS}}\to\irl{L_{MS}}}{\src{\bullet}}$ for the robust preservation of \gls{ms} by composing $\cc{\src{L_{TMS}}\to\trg{L}}{\src{\bullet}}$ and $\cc{\trg{L}\to\irl{L_{MS}}}{\trg{\bullet}}$ is attained.
\Cref{subsec:cs:scct} defines $\obj{L_{CCT}}$ and a compiler $\cc{\irl{L_{MS}}\to\obj{L_{CCT}}}{\irl{\bullet}}$ that robustly preserves \gls{cct}.
Composing it with $\cc{\src{L_{TMS}}\to\irl{L_{MS}}}{\src{\bullet}}$ yields $\cc{\src{L_{TMS}}\to\obj{L_{CCT}}}{\src{\bullet}}$, a compiler that robustly preserves a combination of \gls{ms} and \gls{cct}.
The final compilation chain in \Cref{subsec:cs:opts} defines optimizing compilers performing either \gls{cf} or \gls{dce} and composes them with $\cc{\src{L_{TMS}}\to\obj{L_{CCT}}}{\src{\bullet}}$, giving an optimizing, secure compilation chain.
